### 2016-12-08 Hhh/Hhh.tex
Adding muon reconstruction section

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{sec:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the \Pgt-pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
My work focussed on checks for the \mutau and \etau channels, as well as being
responsible for limit setting for the \Htohh analysis, and performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the \Pgt-pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
My work focussed on checks for the \mutau and \etau channels, as well as being
responsible for limit setting for the \Htohh analysis, and performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

### 2016-12-08 Objects/Objects.tex
Adding muon reconstruction section

\subsection{Isolation}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined isolation variable is defined as:
\begin{equation}\label{eqn:electron_reliso
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
\end{equation}
Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
hadrons associated with the primary vertex and within 
Where \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} hadrons
associated with the primary vertex

Where $P_{T}(\text{charged})$ corresponds to the $P_{T}$ of all charged hadronic candidates,
$E_{T}(\text{photon, neutral})$ to the transverse energy of all photon and neutral hadron candidates, and $\Delta \beta$ is the energy
esitmate of neutral particles due to pileup, which is taken to be 0.5.

\section{Muons}
\label{sec:objects_muo}

>>>>

\subsection{Isolation}
\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined relative isolation variable is defined as:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
\end{equation}
Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
The contribution from neutral particles due to pile--up needs to be subtracted from
this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
CITE SOMETHING!

\section{Muons}
\label{sec:objects_muo}
Muons are reconstructed by combining tracker tracks and tracks
from the muon system \cite{cms-muon-reco}. Two complementary approaches are used for this,
\textit{Global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
tracks reconstructed in the muon system and searches for a matching
tracker track, then re-applies the Kalman filter on the combination
of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
tracks in the inner tracker which pass requirements on momentum to be considered
a muon candidate track. The trajectory is then extrapolated to the muon systems and
considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
Due to the requirement of a single muon segment this method is more efficeint than the global muon
reconstruction for muons with \pT smaller than 5 GeV \cite{cms-muon-reco}.
For muons with \pT greater than 200 GeV, the momentum resolution is improved
by the global muon reconstruction \cite{cms-muon-cosmics-perf}.

The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
for muons with \pT up to 100 GeV and found to range from 1--6\% depending
on detector region. For muons with \pT between 100 GeV and 1 TeV the momentum resolution
was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
%At values of the transverse momentum pT below about 200 GeV/c, the momentum resolution for a muon track is driven by measurements in the silicon tracker. As a particle’s momen- tum increases and the curvature of its corresponding track decreases, however, momentum resolution in the tracker becomes limited by position measurement resolution (including mis- alignment effects). One can then benefit from the large lever arm and 3.8 T magnetic field in the region between the tracker and the muon system by including hits in the muon chambers.

For global muon reconstruction non-muon backgrounds are small,
though there can be small effects from hadronic showers not fully
contained in the \ac{HCAL}. A larger contribution is expected
from real muons originating from for example decays of hadrons. These
backgrounds can be reduced by applying additional identification criteria.

For the analysis presented in chapter CHAPMSSM additional ``Medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
Apart from having passed either the global or tracker muon reconstruction, the fraction
of valid tracker hits must be greater than 49\%. Additional requirements are made on the
$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
position matching, on the kink finder in the inner tracker, and the segment compatibility. The segment
compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
The compatibility of the tracker- and standalone-reconstructed position is evaluated
by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
compatibility there.

To pass the identification, global- or tracker muons
with a large enough fraction of tracker hits must  \textbf{either} 
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon is reconstructed by the global muon reconstruction algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
\item The segment compatibility is $>$ 0.303
\end{itemize}
\textit{or}:
\begin{itemize}
\item The segment compatibility is $>$ 0.451
\end{itemize}

In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
was used, muons were required to pass ``Tight'' identification requirements \cite{cms-muon-reco}. 
The criteria are
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon must be reconstructed by the global muon algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
\item The global track fit must include hits from at least one chamber in the muon system
\item The inner tracker track must be matched to muon segments in at least two muon stations (ie the muon must be reconstructed as a tracker muon too)
\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
\end{itemize}

\subsection{Isolation}
\label{sec:objects_muo_iso}
As described for electrons in section \ref{sec:objects_ele_iso}, placing isolation 
requirements on muons will also reduce backgrounds from misidentified jets and heavy--flavour
decays. The isolation variable used for muons is very similar to the one described for
electrons in equation \ref{eqn:electron_reliso}, however the cone around the direction of the
muon was chosen as $\Delta R = 0.4$ both during Run 1 and Run 2.
